Concurrent Programming with CXL

### 2020-06-29 book/paper.tex
Changing definition of "blocked"

    and cannot make progress without the help of another process.

@@

We call a process \emph{blocked}
\index{blocked process}%
in a state if the process is waiting on a low-level synchronization
variable and cannot make progress without the help of another process.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.

>>>>

    and cannot terminate without the help of another process.

@@

We call a process \emph{blocked}
\index{blocked process}%
in a state if the process is waiting on a low-level synchronization
variable and cannot terminate without the help of another process.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.
